---
title: "Laboratory of Consumer and Business Analytics"
subtitle: "Conjoint analysis - Laptop Dataset"
author: "Nisha Antony, Sander Martins"
date: "27/01/2021"
output: html_document
---

```{r Loading Dataset, include=FALSE}
laptops = read.csv("Dataset/laptops.csv", sep=";")

```

```{r Loading Libraries, include=FALSE}
library(mlogit)
library(dplyr)
library(ggplot2)
library(MASS)
library(lattice)
```

---
#Project Description

The objective of this project is to have an understanding of conjoint analysis and demonstrate some of the conclusion that we be can found using this analysis.

#Summary of all the analysis to be presented
##Dataset description
## Is our dataset balanced?
## Models to fit our data
## Correlated models
## Choosing models
## Preference share of the users
## Are our users homogeneous?
## Product profiles
## Conclusion


##Dataset description
Our dataset represents the generated answers of questionnaires regarding the choice of laptops.

add code here about:
summarizing the data - levels and attributes
Quantity of each attributes
```{r Data description, echo=FALSE}
summary(laptops)
```



## Is our dataset balanced?

```{r echo=FALSE}

xtabs(choice ~ Price, data=laptops)
xtabs(choice ~ RAM, data=laptops)
xtabs(choice ~ Memory, data=laptops)
xtabs(choice ~ Processor, data=laptops)
xtabs(choice ~ Weight, data=laptops)
xtabs(choice ~ ScreenSize, data=laptops)
```

## Models to fit our data

## Correlated models

## Choosing models

## Preference share of the users

## Are our users homogeneous?

## Product profiles

## Conclusion